\documentclass[11pt,twoside,a4paper]{report}
\usepackage{appendix}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{pdfpages}

% set the default, standard, geometry
\geometry{left=25mm, right=25mm, top=25mm, bottom=25mm}

\setlength{\parskip}{\baselineskip}
\clubpenalty10000
\hyphenpenalty10000
\widowpenalty10000

\begin{document}

\title{ID2216 Developing Mobile Applications\\Assignment 3 Report}
\author{Rafael Aldana (rafaelap@kth.se)\\Vincent Delitz (delitz@kth.se)\\Ruth Eriksson (ruthe@kth.se)}
\date{\today}
\maketitle

%\newcommand{\webOrNative}{Web~}

%\begin{abstract}
%During the course, we have worked in team to propose, build, and document a mobile app. We have developed a functional \webOrNative application that addresses an interesting and relevant area we have identified. This report describes step-by-step how we designed the mobile application.
%\end{abstract}

\tableofcontents
\thispagestyle{empty}

%\listoffigures

%\listoftables

\renewcommand{\chaptername}{Assignment}
\setcounter{chapter}{1}
\chapter{WebApp prototype}
\setcounter{page}{1}

\section{WebApp prototype feedback}

After finalizing the WebApp prototype, we showed it to friends in order to gather their feedback. Some of the major feedback points we discovered are listed below:

After finalizing the WebApp prototype, we showed it to friends in order to gather their feedback. Some of the major feedback points we discovered are listed below:

\begin{itemize}

\item In search-overview menu, if I like an offer, should not I be able to click it?

\item Put the calendar widget at the choice for the dates in offer

\item Offer in home and new offer in top menu point to different outcomes, is it what we want?

\item Why overview search returns the query and specify search requires the login?

\item In specify search the top menu is not present, in the other choices it is.

\item If you log out, you should return to home.

\item Is not the top menu too much wide for a smartphone? Should not it be better a couple of big buttons to go home or back?

\end{itemize}

We will tackle this feedback in the next assignment.

We will tackle this feedback in Assignment \ref{assignment:android-prototype}.

\chapter{Android prototype}
\label{assignment:android-prototype}


\end{document}