nes (126 sloc)  7.87 KB
\documentclass[11pt,twoside,a4paper]{report}
\usepackage{appendix}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{pdfpages}

% set the default, standard, geometry
\geometry{left=25mm, right=25mm, top=25mm, bottom=25mm}

\setlength{\parskip}{\baselineskip}
\clubpenalty10000
\hyphenpenalty10000
\widowpenalty10000

\begin{document}

\title{ID2216 Developing Mobile Applications\\ Report}
\author{Rafael Aldana (rafaelap@kth.se)\\Vincent Delitz (delitz@kth.se)\\Ruth Eriksson (ruthe@kth.se)}
\date{\today}
\maketitle
\section{Introduction}
Wecall is an application that wants to make people aware of neglected contacts and help to find small 
windows of opportunity to call and nuture important social connections.
\section{User experrience}
When you open the application you get a good overview of your friends, with pictures, in sections.
Each section is a time frame. This makes it easy to see the contacts you have neglected the most. Alos there
is a suggestion on top of the page. Each section is scrollable, which is not quite obvious at first. 
When you click/tap a contact you can se name, phone number, last time called, address and local time. 
There is also a button for a map feature for the address. The local time feature is verry usefull when 
you have a lot of friends and family abroad. The map is simple and easy to use yet it has some nice extra 
features like the map and the time zone information.
\section{Technical implementaion}
The application was built with Android Studio and Eclipse and based on existing code. It is great that you 
were able to find code to repurpose and extend rather than writing all code from scratch. It is good practice
doing so and hopefully you saved som time and debugging. 
Did you benefit from using two different development tools? Was Eclipse usefull for your purpose?
The application reads phonebook information and references contact data including call logs using manifest.permission
class. This seems to be working with no problem!
From main view users can open detail view of a contact and view address, phone number, and timezone. Users
can initiate a call and click/tap a symbol wich launches location based services offered by Goolge. The three 
implemented interfaces, Google Maps Android, Geocoding and Time Zone seem to work well in the applicationa and look like they
are well integrated. 
\section{Design choices}
Regarding main view, have you thought about making the user able to call a person direct from main view with for example a long click.
That would eliminate the need of loading detail view and the user would save one click/tap and a wait for a load. The scrollable sections
are not obvious/selfexplanatory, maybe a symbol or an arrow that shows the user that you can scroll down or up.
The detail view has information about the contact but the content and the tags melt together because they are the same font and size, 
maybe make one of them bold or larger.
Over all great work and idea. Good luck developing!
